Making Sequential Programs Deterministic

### 2019-03-22 design.tex
Don't use tab characters

	// Client code
	class Client {
	    void test() {
	        @NonDet Random rnd = new Random(); // No error.
	        System.out.println(rnd);                    // Error - println takes @Det arguments.
	        @Det Random rnd1 = new Random();  // Error - subtyping rules violated.
	    }
	}
	\end{verbatim}
	\caption{Example: Errors detected by determinism checker}
	\label{code-determinism}
\end{figure}

>>>>

    // Client code
    class Client {
        void test() {
            @Det double d = Math.random();  // Error - subtyping rules violated.
            @NonDet double nd = Math.random(); // No error.
            System.out.println(nd);                    // Error - println takes @Det arguments.
        }
    }
    \end{verbatim}
    \caption{Example: Errors detected by determinism checker}
    \label{code-determinism}
\end{figure}
